---
title: "Relacion la energia total entregada (KWH) y el nivel de aceite(OLI)"
output: html_notebook
---

```{r}
analizeDb = read.csv("C:\\Users\\Usuario\\OneDrive - Universidad Nacional de Colombia\\Documentos\\NATIONAL UNIVERSITY OF  COLOMBIA\\SEEDBEBS\\Seeds of Statistics\\Data  Anlyze (Edward)\\modeling\\trfmMntr_DB.csv")
View(analizeDb)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}

colums_correlation <-analizeDb[,c("KWH","OLI")]
correlation_matrix <- cor(colums_correlation, method = "pearson")
print(correlation_matrix)
```

```{r}
plot(colums_correlation)
Reg <- lm(analizeDb$OLI ~ analizeDb$KWH)
abline(Reg, col= "red",lwd = 2)

```

```{r}
Reg
summary(Reg)
```

# Modelo  de regresion 

Dado el modelo de regresion $y_i = \beta_0 + B_i x_i + e_i$ :

-   $y_i$ : Variable dependiente : "OLI"

$x_i$ : Variable independiente :"KWH"

$\beta_0$ : intercepto : 36.88

$\beta_i$ : Coeficiente de correlacion : $0.0002174 \quad o \quad(2.174^{e-04}).$

$e_i:$ error : $ei \sim N(0, \sigma^2)$

$$OLI =  36.88 + KMH \cdot 0.0002174 + e_i$$
